---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# quoter

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The `quoter` R package generates a random quote sourced from various sources. You can use this, say, to output an inspirational quote every time your R starts.

## Installation

You can install the released version of quoter with

``` r
remotes::install_github("emitanaka/quoter")
```

## Example

Get a random quote that are sourced from [brainy](brainyquote.com), [statquotes](https://github.com/friendly/statquotes) or [dadjoke](https://github.com/jhollist/dadjoke).

```{r example}
quoter::quotes(source = "brainy")
```

You can get a decorated one. The color output will show on terminal.

TODO: need to add dark/light themes. Also ability to customise output easily.

```{r }
quoter::decorate(quoter::quotes())
```

## Show quote on R start-up

To show quote on R start-up, you will need a special function ot the `.Rprofile` file. The easiest way to access the `.Rprofile` is to use 
```{r, eval=F}
usethis::edit_r_profile()
```

In the `.Rprofile` file add below to get a quotation for every start-up.
```{r, eval=F}
.First <- function() {
  quoter::decorate(quoter::quotes())
}
```


